A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-18 PPSN2016/paper.Rnw

\begin{abstract}
In a volunteer distributed computing system, users run a program in
their own machine to contribute to a common effort. If the program is
embedded in a web page, collaboration is easy, but also ephemeral. In
this paper we analyze a volunteer evolutionary computing system called
NodIO, trying to find out a few rules that encourage volunteer
participation and how to make the most of their contributions to the
evolutionary algorithm. We will show different measures of
participation and contribution to the algorithm and how different
volunteer usage patterns and tweaks in the algorithm contribute to
improvements and leveraging of these contributions. 
\end{abstract}

>>>>

\begin{abstract}
In a volunteer distributed computing system, users run a program on
their own machine to contribute to a common effort. If the program is
embedded in a web page, collaboration is easy, but also ephemeral. In
this paper, we analyse a volunteer evolutionary computing system called
NodIO, trying to find out a few rules that encourage volunteer
participation and how to make the most of their contributions to the
evolutionary algorithm. We will show different measures of
participation and contribution to the algorithm and how different
volunteer usage patterns and tweaks in the algorithm contribute to
%Pablo: añadiría un ", such as...," con un ejemplo entre "algorithm" y "contribute"
improvements and leveraging of these contributions. 
\end{abstract}
